Basics of Hardware Cache Optimization

### 2017-06-19 tex/list-vs-vector.tex
Add TikZ graphic representing an array of pointers

\subsection{``True OO Style''}

@@

In object-oriented systems, objects are typically referred to by pointers to a common base
class.  A polymorphic container of such pointers allows for dynamic dispatch of virtual
functions.  This carries the risk of degrading the \x{superior} performance of a
sequential data structure to that of a list.

TODO: create an illustration with TikZ.
\begin{tikzpicture}
\node [draw] (object1) {};
\end{tikzpicture}

TODO~\cite[42:00]{stroustrup-talk}.

>>>>

\subsection{``True'' OO Style}

@@

In object-oriented systems, objects are typically referred to by pointers to a common base
class.  A polymorphic container of such pointers allows for dynamic dispatch of virtual
functions.  However, this carries the risk of degrading the \x{superior} performance of a
sequential data structure to that of a list%
% ~\cite[\href{https://youtu.be/0iWb_qi2-uI?t=51m22s}{51:22}]{stroustrup-talk}.
~\cite[51:22]{stroustrup-talk}.
See \cref{fig:true-oo}.

\begin{figure}
   \centering
   \input{tex/oo-picture}
   \captionsetup{width=.9\linewidth} % FIXME: hacks!
   \caption[Array of Pointers]{Array of Pointers; while the array is compact, the actual
   objects may not be laid out sequentially in memory.}
   \label{fig:true-oo}
\end{figure}
